The demographic costs of sexually antagonistic selection in partially selfing populations

### 2022-01-29 doc/SA-Hermaphrodites-wDemography-R1.tex
Add Dryad reviewer link to ms

\textit{Online enhancements}: Dryad digital repository ({\itshape https://doi.org/10.5061/dryad.c2fqz619t}).

@@

Here, we briefly describe a matrix model incorporating multiple life-cycle stages and a single diallelic locus under SA selection on male and female fertility for populations of partially-selfing simultaneous hermaphrodites. We focus our presentation on a two-stage example of the model and discuss its' underlying biological assumptions. The derivation of the general model for any number of age or stage classes is provided in the Online Supplementary Material. The derivation follows closely the logic presented in \citet{deVriesCaswell2019a, deVriesCaswell2019b}, and in fact, it reduces to the two-sex stage-structured model of \citet{deVriesCaswell2019a} under obligate outcrossing (when selfing is not allowed). All computer code and data necessary to reproduce the results are available on Dryad (\url{https://doi.org/10.5061/dryad.c2fqz619t}) and on GitHub (\url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}).

@@

\citet{LeeKelly2015} also report greenhouse pollen viabilty data for several mapping populations of {\itshape M.~guttatus}, which includes data for inv6 homozygotes, from which relative fertilities can be estimated. We chose to use the field estimated pollen viability and flower number data, despite the lack of inv6 homozygotes, because it probably gives a more accurate reflection of the fitness effects of inv6 in the field. Moreover, both approaches require making assumptions regarding the dominance effects of inv6. Given the obvious pitfalls of estimating selection on inv6 from the available data, it goes without saying that the location of inv6 in demographically viable polymorphic parameter space is a highly speculative, but nevertheless interesting, proof of concept for our model predictions. Supplementary data files showing how selection coefficients were calculated are publicly available on Dryad (\citealt{Olito-DeVries-2022-Dryad}; \url{https://doi.org/10.5061/dryad.c2fqz619t}).

>>>>

\textit{Online enhancements}: Dryad digital repository ({\itshape https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}).

@@

Here, we briefly describe a matrix model incorporating multiple life-cycle stages and a single diallelic locus under SA selection on male and female fertility for populations of partially-selfing simultaneous hermaphrodites. We focus our presentation on a two-stage example of the model and discuss its' underlying biological assumptions. The derivation of the general model for any number of age or stage classes is provided in the Online Supplementary Material. The derivation follows closely the logic presented in \citet{deVriesCaswell2019a, deVriesCaswell2019b}, and in fact, it reduces to the two-sex stage-structured model of \citet{deVriesCaswell2019a} under obligate outcrossing (when selfing is not allowed). All computer code and data necessary to reproduce the results are available on Dryad (\url{https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}) and on GitHub (\url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}).

@@

\citet{LeeKelly2015} also report greenhouse pollen viabilty data for several mapping populations of {\itshape M.~guttatus}, which includes data for inv6 homozygotes, from which relative fertilities can be estimated. We chose to use the field estimated pollen viability and flower number data, despite the lack of inv6 homozygotes, because it probably gives a more accurate reflection of the fitness effects of inv6 in the field. Moreover, both approaches require making assumptions regarding the dominance effects of inv6. Given the obvious pitfalls of estimating selection on inv6 from the available data, it goes without saying that the location of inv6 in demographically viable polymorphic parameter space is a highly speculative, but nevertheless interesting, proof of concept for our model predictions. Supplementary data files showing how selection coefficients were calculated are publicly available on Dryad (\citealt{Olito-DeVries-2022-Dryad}; \url{https://datadryad.org/stash/share/81sAuXGEg8cSh-S9VVL0PfBCsl6YLkG1OIFBCvOefac}).
